\chapter*{Acknowledgements}
\begin{spacing}{1.3}
This research would not have been possible if it was not for the trust, guidance and support of Dr. Marco Ruffini even at times that he would find me napping on my desk or spending more hours outside the red door than behind my desk. The invaluable inputs of Dr. Hamed Ahmadi, Dr. Irene Macaluso, Dr. Luiz Da Silva have also greatly impacted this research.


I want to express my gratitude to the \textit{Irish Taxpayers} and Science Foundation of Ireland for making this research possible.


My sincere gratitude also goes to the following wonderful people:

My family away from home, Goli (for being my rock), Ramisa (for her unconditional kindness), Azadeh, Sabrina, Melika, Abdullah, Ali, and Alireza.


To my loyal friends back home in Iran who did not stop their love and support after years being apart. To name a few, Saeed, Marjan, Sufi, Hadi, Leila, Yalda, Sama, Farahani, Naghash, Parisa, Negin, Mohsen, Bahar, and Mojtaba.

To the CouchSurfing community for being my safespace on Friday nights, Martina, Chiara, Craig, Sam, Eliza, Lorena, Ashley, Cáit, Aniruddha, Treasinha, Gearóid, Delfi, Katri, Natalia, Lilly, Lina, Liz, Jurek, Ilia, Ula, Alice, Simon.

All the fantastic people in Dunlop Oriel House: Stefan (for his irreplaceable company), Harleen, Erika and Joao (for bringing joy to the Lab), Conor and Danny (the lab's grammar gurus), Eamonn (the most caring), Fadhil (my brother in arms), Francisco, Parna, Arman, Harun, Merim, Jernej, Pedro, Johnathan, Tom, Ramy, Alan, Andrea, Emanuele, Carlo, Nicola, Jacek, Elma, Yi, Boris, Andrei, Diarmuid, Maicon, Sandip, Indirakshi, Jessica, Haris, Christian, George, Jean, Alessandro, Davi, Natal, Ana, Matias, Ramiro, Adam, Johan, Avishek, Dennis, Atri, Frank, Sanwal, and Aleksandra.

CONNECT's administrative staff Monica, Andrew, Ruth, Cathrine, Lassane, David, Tim, Collette, Linda, Kevin, Raquel, Shirley, Martin, and Seán for my o.

To \textit{Chapter}, the wounded pigeon who found me on the cold Christmas day in Dublin and kept my company during the thesis writing journey.

Most Importantly, my parents, for their love and support, my sister Negar, my niece Fereshteh, Mehdi, for encouraging me and my late grandfather, Dr. Jalai, who was a source of inspiration.
% To my examiners,

\end{spacing}
